---
title: "Data_Anaylsis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data_Anaylsis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library Install
```{r}
library(dplyr)
```


# Loading of files
```{r}
Eye_Contact <- read.csv(file = "../data-raw/Raw Data/EyeContact_Data.csv")
Gesture <- read.csv(file = "../data-raw/Raw Data/Gesture_Data.csv")
Inhibitory_Control <- read.csv(file = "../data-raw/Raw Data/InhibitoryControl_Data.csv")
Summary <- read.csv(file = "../data-raw/Raw Data/Summary_Data.csv")
Temperament <- read.csv(file = "../data-raw/Raw Data/Temperament_Data.csv")
Working_memory <- read.csv(file = "../data-raw/Raw Data/WorkingMemory_Data.csv")
```

# Various of tests
```{r} 
Eye_Contact
Gesture
Inhibitory_Control
Summary
Temperament
Working_memory
```

```{r, echo = FALSE}
Complete_Data_Wolf <- inner_join(Eye_Contact, Gesture, Inhibitory_Control, by = "Name") %>% inner_join(Summary, Temperament, by = "Name") %>% inner_join(Working_memory, by = "Name") %>% filter(Species.x == "Wolf")
```

```{r, echo = FALSE}
Complete_Data_Dog<- inner_join(Eye_Contact, Gesture, Inhibitory_Control, by = "Name") %>% inner_join(Summary, Temperament, by = "Name") %>% inner_join(Working_memory, by = "Name") %>% filter(Species.x == "Dog") 
```

```{r, echo = FALSE}
str(Complete_Data_Dog)
```

```{r, echo = FALSE}
str(Complete_Data_Wolf)
```

# Mean/Median/Standard Deviation for Dog's Eye Contact interactions time/sec.
```{r}
Complete_Data_Dog |>
  summarize(xbar = mean(Complete_Data_Dog$Eye.Contact, na.rm = TRUE), median = median(Complete_Data_Dog$Eye.Contact, na.rm = TRUE), s = sd(Complete_Data_Dog$Eye.Contact, na.rm = TRUE))
```

# Mean/Median/Standard Deviation for Wolf's Eye Contact interactions time/sec.
```{r}
Complete_Data_Wolf |>
  summarize(xbar = mean(Complete_Data_Wolf$Eye.Contact, na.rm = TRUE), median = median(Complete_Data_Wolf$Eye.Contact, na.rm = TRUE), s = sd(Complete_Data_Wolf$Eye.Contact, na.rm = TRUE))
```

```{r}
boxplot(Complete_Data_Wolf$Eye.Contact, Complete_Data_Dog$Eye.Contact, main = "Wolf vs Dogs: Eye-Contact", xlab = "Species", ylab = "Contact per sec", col = c("red", "brown"), names = c("Wolf", "Dog"), horizontal = TRUE)
```

# Succees Rate of Wolfs finding food within a route without touching transparent walls
```{r}
Inhibitory_Control |> filter(Species == "Wolf") %>% 
  summarize(xbar = mean(Correct/Trial, na.rm = TRUE), median = median(Correct/Trial, na.rm = TRUE), s = sd(Correct/Trial, na.rm = TRUE))
```

# Succees Rate of Dogs finding food within a route without touching transparent walls 
```{r}
Inhibitory_Control |> filter(Species == "Dog") %>% 
  summarize(xbar = mean(Correct/Trial, na.rm = TRUE), median = median(Correct/Trial, na.rm = TRUE), s = sd(Correct/Trial, na.rm = TRUE))
```

```{r, echo = FALSE}
Inhibitory_Control %>% filter(Species == "Dog") -> Inhibitory_Control_Dog
Inhibitory_Control %>% filter(Species == "Wolf") -> Inhibitory_Control_Wolf
```


```{r, echo = FALSE}
boxplot(Inhibitory_Control_Wolf$Correct/Inhibitory_Control_Wolf$Trial, Inhibitory_Control_Dog$Correct/Inhibitory_Control_Dog$Trial, main = "Wolf vs Dogs: Senses", xlab = "Species", ylab = "Chance % of bumping into transparent walls to each to food", col = c("red", "brown"), names = c("Wolf", "Dog"), horizontal = TRUE)
```

```{r}
Working_memory |> filter(Species == "Dog") %>% 
  summarize(xbar = mean(Trials, na.rm = TRUE), median = median(Trials, na.rm = TRUE), s = sd(Trials, na.rm = TRUE)) 
```

```{r, echo = FALSE}
Working_memory %>% filter(Species == "Dog") -> Working_memory_Dog
```

```{r, echo = FALSE}
Working_memory %>% filter(Species == "Wolf") -> Working_memory_Wolf
```


```{r}
Working_memory |> filter(Species == "Wolf") %>% 
  summarize(xbar = mean(Trials, na.rm = TRUE), median = median(Trials, na.rm = TRUE), s = sd(Trials, na.rm = TRUE))
```

```{r}
boxplot(Working_memory_Wolf$Trials, Working_memory_Dog$Trials, main = "Wolf vs Dogs: Memory", xlab = "Species", ylab = "Numbers of attempts to complete memory test", col = c("red", "brown"), names = c("Wolf", "Dog"), horizontal = TRUE)
```

# Paired T-Test
```{r}
Wolf_Test_Memory <- c(rnorm(100, mean = 11.15385, sd = 6.398077	))
Wolf_Test_Eye_Contact <- c(rnorm(100, mean = 1.736667, sd = 2.259502))
t.test(Wolf_Test_Memory, Wolf_Test_Eye_Contact, paired = TRUE)
```
* Wolf's ability to maintain eye contact with an individual does have an association to their memory capabilities. 

```{r}
Dog_Test_Memory <- c(rnorm(100, mean = 11.25581, sd = 7.000316	))
Dog_Test_Eye_Contact <- c(rnorm(100, mean = 4.705909, sd = 4.663277))
t.test(Dog_Test_Memory, Dog_Test_Eye_Contact, paired = TRUE)
```
* Dog's ability to maintain eye contact with an individual does have an association to their memory capabilities. 
